The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-11-21 paper/mri_paper.tex
defined terms
typos and define gas pressure
fixed typo in streamfunction description

@@

We define the flux function $A$ and streamfunction $\Psi$. $A$ is the familiar two-dimensional vector potential. $A$ and $\Psi$ are scalar fields defined as the curl of the magnetic field and velocity, respectively, and so automatically satisfy our constraints.

>>>>

In the above, $P$ is the gas pressure, $\nu$ is the kinematic viscosity, $\eta$ is the microscopic diffusivity, $\nabla\Phi$ is the gravitational force per unit mass, and the current density is

\beq
\mathbf{J} = \frac{2}{\beta}\nabla\times\mathbf{B}.
\eeq

@@

We define the flux function $A$ and streamfunction $\Psi$. $A$ is the familiar two-dimensional vector potential. $A$ and $\Psi$ are scalar fields. The curl of $A$ and the curl of $\Psi$ are defined as the magnetic field and velocity, respectively, and so $A$ and $\Psi$ automatically satisfy our constraints.
